Application-Level Regression Testing Framework using Jenkins

### 2017-03-28 manuscript/manuscript.tex
Finished draft of web config section.

We decided to use Apache HTTPD Server as the front-end web server facing the world. To achieve that, first we set Jenkins web server to only listen to \texttt{localhost} interface on port 8080, by setting the following variable in Jenkins configuration file \texttt{/etc/sysconfig/jenkins}:
FIXME: COPY RELEvANT JENKINS CONFIG HERE

Second, we need to forward all HTTP requests to Jenkins, and also forward Jenkins responses back to the client. This is a feature called ''ReverseProxy`` in Apache HTTPD. Th

>>>>

We decided to use Apache HTTP Server as the front-end web server facing the world. To achieve that, first we set Jenkins web server to only listen to \texttt{localhost} interface on port 8080, by setting the following variable in Jenkins configuration file \texttt{/etc/sysconfig/jenkins}:
\begin{lstlisting}
#-- Restrict to only listen to localhost
JENKINS_PORT="8080"
JENKINS_LISTEN_ADDRESS=127.0.0.1
\end{lstlisting}

Second, we need to forward all HTTP requests to Jenkins, and also forward Jenkins responses back to the client. This is accomplished using the module \texttt{mod_proxy} (FIXME: Add Reference) in Apache HTTP which allow it to act as a proxy / gateway. To enable this feature, the following stanza is added to the configuration file \texttt{/etc/httpd/conf.d/ssl.conf} inside the \texttt{<VirtualHost>} directive:

\begin{lstlisting}
ProxyRequests       Off
ProxyPreserveHost   On 
AllowEncodedSlashes On 
<Proxy *>
  Order deny,allow
  Allow from all  
</Proxy>
ProxyPass         /  http://localhost:8080/ nocanon
ProxyPassReverse  /  http://localhost:8080/
ProxyPassReverse  /  http://bwjenkins.ncsa.illinois.edu/
RequestHeader set X-Forwarded-Proto "https"
RequestHeader set X-Forwarded-Port "443"    
\end{lstlisting}

With this setup, all requests to the HTTP over SSL protocol (i.e. \texttt{https}) on port 443 by default) are forwarded to Jenkins server and Jenkins reponses are forwarded back to the client (i.e. web browser).

Optinally, one may allow non-authenticated, ''read-only`` access to Jenkins dashboard over regular (non-secure) HTTP connection. Jenkins' own authorization mechanism can be used to control this access, but we can also add Apache HTTP directives for further security, limiting \texttt{GET} requests. To achieve this, we created the file \texttt{/etc/httpd/conf.d/vhosts.conf} with the following content:
\begin{lstlisting}

NameVirtualHost *:80
<VirtualHost *:80>

  ServerAdmin tbouvet@illinois.edu
  DocumentRoot /var/www/html
  ServerName bwjenkins.ncsa.illinois.edu
  Options Indexes FollowSymLinks

  ProxyPass / http://localhost:8080/ nocanon
  ProxyPassReverse  /  http://localhost:8080/
  ProxyRequests Off
  AllowEncodedSlashes On

  LimitRequestBody 512
  LimitRequestFields 15
  LimitRequestFieldSize 1024
  LimitRequestLine 128

  <Location /asynchPeople/>
    Order Deny,Allow
    Deny from all
  </Location>

  <Proxy *>
    Order deny,allow
    Allow from all
    <LimitExcept GET>
      Deny from all
    </LimitExcept>
  </Proxy>

</VirtualHost>

\end{lstlisting}
